---
title: "index"
author: "Mayumi, Erica, Anush, Jalen"
date: "11/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homelessness in the United States

**Overview**

We will be exploring the field/domain of homelessness and mental health to humanize the homeless population that is ever so present yet invisible to our society. We want to show the inevitability and causes of homelessness and create empathy for those suffering from it. At the same time, we would like to be responsible with our data and not reduce our subject to their conditions, which is why we are committed to researching their interpersonal conditions.

```{r include= FALSE}
# Here are some comments
source("summary_project.R")
```
**Summary**

The data we gathered to analyze is from [The U.S. Treasury Data Lab](https://raw.githubusercontent.com/info201b-au20/project-ereyand/gh-pages/panel_2_table_and_counts_v7_2020_03_27.csv). This dataset contains a significant amount of information that illuminates the complexities of homelessness and the number of people that experienced it at the time this data was collected. The data set contains `r format(summary_info$obs_national)` in which each row represents a county in the United States where this information was gathered. 

Thanks to this data, we were able to analyze which county has the lowest homeless population which is `r format(summary_info$city_lowest)` and which has the highest (`r format(summary_info$city_highest)`) out of the total `r format(summary_info$total_homeless_individual)` individuals experiencing homelessness in the United States.

The dataset is organized in such a concise manner that we were able to find out that there's six counties that have the highest percentage of its homeless population **in shelters** in the entirity of the U.S. which are `r format(summary_info$highest_prop_in_shelters)`. While `r format(summary_info$highest_demand_for_shelters)` has the highest demand for shelters since its the city that has the most amount of people out of shelters meaning there isn't enough space for their citizens. 

Based on the dataset, `r format(summary_info$highest_chronically_homeless_city)` is the city where there's the most chronically homeless people and `r format(summary_info$highest_youth)` has the highest amount of youths (people under 25) experiencing homelessness. 

Unfortunately, historically there's a large number of veterans experiencing homelessness; `r format(summary_info$highest_veterans)` has the highest amount of homeless vets.

There's many counties that have a high demand for homeless shelter spots for veterans, in total there are 61. The following counties are abbreviated to represent a county in the United States based on the state abbreviation and the corresponding number: `r format(summary_info$highest_veterans_in_shelters)`. These counties have the highest number of homeless veterans waiting for a spot in shelters.

Consequently, there isn't always enough space for people in homeless shelters, `r format(summary_info$highest_demand_for_veterans)` is the city that has the most unsheltered homeless veterans in the country. 


**Dataset we analyzed**
```{r kable_example, echo = FALSE}
library("knitr")
# national <- read.csv("https://raw.githubusercontent.com/info201b-au20/project-ereyand/gh-pages/panel_2_table_and_counts_v7_2020_03_27.csv")
# kable(national)
homelessness_summary
```

The "homelessness_summary" chart is a cleaned up version of the summary project and original dataset, outlining the total homeless in each state regarding the CoC's, and was intended to show the relationship between veterans and homelessness, as well as populations and homelessness. 

**Chart One**
```{r include= FALSE}
# Here are some comments
source("first_chart.R")
```
### Homeless Veterans in the West Coast
```{r}
  wa_plot
  ca_plot
```
We decided to focus on veterans who are experiencing homelessness in the United States. Unfortunately, this is still a large dataset so we decided to separate it into different regions of the country; the West coast (which will be represented with these charts), the Northern & Southern region, and the East coast. Additionally, we focused on veterans that were able to seek assistance in shelters and those who were unable due to capacity constraints, the term we use for this demographic is _unsheltered_. Our questions correlate to these specifications, _chart one is on sheltered/unsheltered veteran in the West coast_. The charts we created for these two states show a sad reality, there's a signficant amount of homeless veterans who are unsheltered. the `wa_plot` illuminates how this number is in the hundreds for Washington state. But, the `ca_plot` shows how for California, the number of unsheltered homeless veterans is in the *thousands*.

**Chart Two**
```{r include= FALSE}
# Here are some comments
source("second_chart.R")
```
### Homeless Veterans in Northern and Southern U.S.
```{r}
  mi_plot
  tx_plot
```
We wanted to see if there were any similarities between the number of veterans experiencing homelessness in the Northern part of the country and the Southern part of the country. We did this by analyzing homeless data in Minnesota and Texas, both are states that are adjacent to one of the United States' bordering countries (Canada and Mexico). Sadly with so many people experiencing homelessness, the reality is that there isn't enough space for everyone in shelters so we wondering _if there were drastic differences between sheltered and unsheltered homeless veterans in Northern/South U.S.A.._ Our hypothesis in regards to the question these charts answered is correct since `tx_plot` show how there's significantly more unsheltered veterans in Texas than in Minnesota. We believe this is because Texas is seen more patriotic, that this would correlate to more military service members residing in this state and therefore a higher percentage of homeless veterans.

**Chart Three**
```{r include= FALSE}
# Here are some comments
source("third_chart.R")
```
### Homeless Veterans in the East Coast
```{r}
  ny_plot
  fl_plot
```
Lastly, we gathered the data from two east coast states; New York and Florida. These states have many differences that vary geographically, demographically, economically, etc. The charts tell us that sadly, many homeless veterans aren't able to seek refuge in shelters due to capacity. In the `fl_plot`, we can see how significantly more veterans are unsheltered because while the data is more varied, there's a different scale on the x-axis. This is very interesting since initially, we believed that the state with the higher population would have a higher percentage of unsheltered veterans (in regards to the East coast).
