---
title: "index"
author: "Mayumi, Erica, Anush, Jalen"
date: "11/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
**In the Markdown document you create, you should run the other scripts to generate the necessary content your report:**

**Write an introductory paragraph explaining the domain/data set (feel free to borrow from the project proposal)**

We will be exploring the field/domain of homelessness and mental health to humanize the homeless population that is ever so present yet invisible to our society. We want to show the inevitability and causes of homelessness and create empathy for those suffering from it. At the same time, we would like to be responsible with our data and not reduce our subject to their conditions, which is why we are committed to researching their interpersonal conditions.


**Write a summary paragraph that includes information calculated by your summary information function**

The information we gathered from sdjfjdf


**Render your table and describe pertinent observations found in it**
```{r kable_example, echo = FALSE}
library("knitr")
national <- read.csv("https://raw.githubusercontent.com/info201b-au20/project-ereyand/gh-pages/panel_2_table_and_counts_v7_2020_03_27.csv")
kable(national)
```

**Describe the purpose of each chart (e.g., "this chart was intended to show the relationship between..."), render each chart, and describe pertinent observations found in each chart**

Each chart kjsdhfkjhsk